### 2020-08-30 la/c1.tex
WIP 31Aug2020

\item Let $\alpha\beta = 0$. If $\alpha \ne 0$ then $\alpha^{-1}$
exists. Multiply both sides of the equation by $\alpha^{-1}$ to get
$\beta = 0$. Similarly, $\beta \ne 0$ gives $\alpha = 0$. The equality
is also true when both $\alpha$ and $\beta$ are zero.
\end{enumerate}
\end{enumerate}

>>>>

\item Let $\alpha\beta = 0$. If $\alpha \ne 0$ then $\alpha^{-1}$
exists. Multiply both sides of the equation by $\alpha^{-1}$ to get
$\beta = 0$. Similarly, $\beta \ne 0$ gives $\alpha = 0$. The equality
is also true when both $\alpha$ and $\beta$ are zero.
\end{enumerate}

\item
\begin{enumerate}
\item The set of all integers is not a field because the inverse
under addition does not exist.
\item The set of all integers is a group. It is not a field because
multiplicative inverse does not exist.
\end{enumerate}

\item Given $m \in \soi$ and $Z_m = \{0, 1, \ldots, m - 1\}$, the 
field operations are defined as $\alpha \oplus \beta = (\alpha + 
\beta)\mod n$ and $\alpha \odot \beta = (\alpha\cdot\beta)\mod n$.
The set $(Z_m, \oplus)$ is an abelian group. However, $(Z_m, \odot)$
has an inverse if and only if $m$ is prime.
\end{enumerate}
